Project Notes

### 2020-02-10 StateOfPractice/Peter-Notes.tex
reusability, portability

@@

Issues in the Specification and Measurement of Software Portability (Mooney)\\

Designing a Measurement Method for the Portability Non-functional Requirement (Talib)\\

@@

https://www.softwaretestinghelp.com/what-is-portability-testing/ 
\end{document}

>>>>

Taxonomy of reusability mctrics
1. Empirical methods
-
-
Module oriented
- Complexity based
- Size based
- Reliability based
Component oriented

 2.Qualitative methods
-
-Module oriented
- Style guidelines
Component oriented
- Certification guidelines
- Quality guidelines\\

-----

@@

Issues in the Specification and Measurement of Software Portability (Mooney):\\
The term portability
 refers to the ability of a software
 unit to be ported (to a given environment).
 A program is
 portable if and to the degree that the cost of porting is less than
 the cost of redevelopment. A software unit would be perfectly
 portable if it could be ported at zero cost, but this is never
 possible in practice.
 Instead, a software unit may be
 characterized by its degree ofportability,
 which is a function of
 the porting and development costs, with respect to a specific
 target environment.\\

 Some of these issues have been examined by the author
 [Mooney 931. This work has proposed as a metric the degree of
 portability
 of a software unit with respect to a target
 environment, defined as
 DPfsu) = 1 - (Cport(su,q) I Crd$\&$req.e2)).\\
 This metric relates portability to a ratio between the cost
 of porting (which depends on the properties of the existing
 software unit and on the target environment), and the cost of
 redevelopment (which depends on the requirements and the
 target environment). A series of experiments is underway to
 refine and validate this metric and to determine how to measure
 or estimate Cpoyf and Crdev.
 One study by Sheets [94]
 suggests that the metric can be badly skewed by secondary
 elements such as inadequate documentation for the existing
 software.\\

Designing a Measurement Method for the Portability Non-functional Requirement (Talib):\\
 EffortNew is the total effort needed in working hours units
 to develop the software functionalities on a new
 environment\\

-----------\\
https://www.softwaretestinghelp.com/what-is-portability-testing/:\\

@@

check Installability, Adaptability, Replaceability, Compatibility or Coexistence\\

Installability: validate OS reqs, memory and RAM reqs, clear installation and uninstallation procedures, additional prerequisites\\

Adapatability: hardware and software dependency, language dependency and communication system\\

\end{document}
